MC-based feasibility study of new sampling calorimeter for measuring the $\gamma$ incident

### 2022-01-04 paper.tex
updates

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{lineno}
\usepackage{xspace}
\usepackage{cleveref}

@@

\begin{document}
\setcounter{page}{0}
\title[]{ MC-based feasibility study of new sampling calorimeter for measuring the $\gamma$ incident angle }

@@

\section{Motivation}
\label{sec:mot}
The electromagnetic calorimeter (EM-Cal) has played an important role in experimental studies of the nuclear and particle physics.  
% experiments specially to detect gamma. 
Various crystals have been developed for better energy and timing resolution of the calorimeter so far~\cite{Calorimeter}. %The most important properties of the detector are good energy and timing resolution, and various crystals has been developed for the purpose[] .
On the other hand, the sampling calorimeter tends to replace the crystal calorimeter in large-scale high energy experiment mainly due to its cost-effectiveness. The sampling calorimeter consists of alternating passive converters that generate the electromagnetic shower and active counters that detect shower particles.

Since the energy deposit into the passive convert can not be measured, its fluctuation called as sampling fluctuation determines the energy resolution of the sampling calorimeter which is generally worth than that of the crystal one.
%mainly determined by the  which causes a limitation of energy resolution,  
%Even though the energy deposit in the passive converter is not detected which is related to the 
%measuring energy deposit of the shower particles tends to replace the crystal calorimeter in large-scale high energy experiment[].
%Due to the fluctuation of energy deposit in the converter, sampling fluctuation, the sampling calorimeter suffers poor energy resolution. 
However, the shower generation becomes more effective by selecting freely among the large numbers of candidate. The active counter can be selected as an easily fabricated in large size with relatively low cost such as the plastic scintillator~\cite{E391a_barrel}. %In addition, the fluctuation becomes not so important for high energy gammas owing to large number of shower particles. %When we use a plastic scintillator as a counter, we can fabricate a large scale of calorimeter with relatively low cost.  
%There are many efforts to develop new types of calorimeter, and a fine-segmented sampling calorimeter is in the line[].

A layer structure of the sampling calorimeter enables us to measure the profiles of shower particles in layer by layer along to the shower development. That is, we can estimate the direction of incident gamma by connecting the center of each profile. We studied a possible detector configuration to measure incident direction of gamma with energies in a range from hundred MeV to few GeV. 
%measure not only energy but also incident angle of photon. Considering a stochastic process in shower generation, there is a certain limitation of the detection resolution. Also, the effect of the sampling fluctuation is a matter in medium energy photons in range 100 MeV to few GeV photons. 
Even though the sampling fluctuation makes limitation on the energy resolution of the calorimeter in this energy range, there is an experiment to have a motivation on developing a detector configuration enable to measure the incident direction.

@@

Considering negligible detection efficiency on neutrinos, the $K_L \rightarrow \pi^0 \nu \bar{\nu}$ decay is defined as an event existing only single $\pi^0$ in the final sate, which is reconstructed by detecting two gammas generated from prompt decay of the $\pi^0$. The KOTO utilizes undoped Cesium Iodide (CsI) crystals as an EM-Cal to measure the gamma~\cite{CsI}. %An hermetic detector system surrounding decay region confirms that there is no any particles accompanying the two photons. 
For the reconstruction, we need an assumption that the two gammas are generated from a single $\pi^0$ decaying at the beam axis in addition to the detection variables. This means that we would get a wrong $\pi^0$ in case the assumption is not correct any more, but there is no information to figure out, unfortunately. With a new information, incident angle, we can judge a validity of the reconstructed $\pi^0$.
%In order to reconstruct a  $\pi^0$ from obtained information of the two gammas 
%In reality, energies and positions of two photons measured at the EM-Cal are not enough to reconstruct the $\pi^0$, and we need an assumption that they are generated from the $\pi^0$ decaying at the beam axis. This reconstruction would be failed in case the assumption is not correct any more, but there is no information to figure out, unfortunately. 
% In addition to the current reconstruction of $\pi^0$, we can extract its decay position independently with the angle measurement. By requiring a consistency between two vertices reconstructed with different observables, we can select genuine single $\pi^0$ decay rejecting wrong pairs due to various sources such as odd-pairing of $K_L \rightarrow \pi^0 \pi^0$ decays, neutron induced two clusters, and so on. It also enables us to remove $\pi^0$ and $\eta$ decays produced by halo neutrons because they occur far from the beam axis. We can expect similar rejection against $K_L \rightarrow \gamma \gamma$ decays when the $K_L$ deviate form the beam center due to scattering.

%For the angle measurement of gamma, we should get information about the spatial profile of shower particles generated in the EM-Cal. This will be realized by recording energy deposit to the cell of detector separately, which are finely segmented in three dimensions. 
We studied a sampling calorimeter consisting of alternating lead sheets and strips of plastic scintillator for the angular measurement of incident gamma. %could be a good candidate of the calorimeter as describe in this paper.
In the following section, the configuration of detector and the reconstruction of $\gamma$-incident angle will be described. The discussion on the optimal configuration and its expected performance will be followed.

\section{Method}
We started the study with a setup of sampling calorimeter consisting of alternating lead sheet as the passive converter and strips of the plastic scintillator as the active counter. % as shown in Fig.~\ref{fig:det_conf}. The electromagnetic shower mainly generated at the lead sheet (passive component) due to its short radiation length ($X_0 = 5.6~{\rm mm})$ and the information of the shower particles is obtained by using the scintillator (active  component). 
The thickness of lead is 1 mm and scintillator is 5 mm, respectively. The lead sheet has a cross-section of  500 mm $\times$ 500 mm and the scintillator strip of 500 mm $\times$ 15 mm being arranged along the X- and Y-direction alternatively along Z-direction as shown in  Fig.~\ref{fig:det_conf}. The generated photon moves along with Z-direction and its incident angle was defined as a polar angle to the direction.  With the configuration, we can get shower profiles in X- and Y-axis in turn, and estimate the incident angle from them. The number of alternating layers is 105, corresponding to 20 radiation length (Xo), in order to contain shower particles fully. The electromagnetic showers are generated with given detector setup by using the GEANT4 package (ver. xxx) with the standard EM sub-packages ~\cite{GEANT4}.

@@

@@

In order to reconstruct the incident angle of the gamma, we used the $\XGB$, which is one of the popular machine learning packages supporting a scalable tree boosting system~\cite{xgboost:2016}. Input data for the $\XGB$ are deposit energies on each scintillator strip by the generated shower particles. It includes the strips of zero-energy deposit in order to satisfy the requirement that the number of input data should be identical. As the training procedure, the $\XGB$ studies profiles of energy deposit to the individual strips with respect to the incident angle for a given $\gamma$ energy.

There are five hyper parameters which can be optimized by user, and their values are selected to provide the best angular resolution as described in table~\ref{tab:XgbPar}. Among the parameters, the Max. depth rapidly improves the angular resolution with increasing its value until 15. The N\_estimators also improves the angular resolution with increasing its number, which is correlated to the value of the Max. depth. Its optimal condition becomes 1000 when the Max. depth is 15.

For the training procedure, gammas are generated uniformly in the range 0 to 50 degrees of polar angle ($\theta$) and  0 to 360 degrees of azimuthal angle. The performance of the angular reconstruction is tested with independently generated data samples with fixed $\theta$ and uniform $\varphi$ from 0 to 360 degrees.

@@

\section{Results}
\label{sec:res}

\subsection{Properties of generated shower}
% moliere rad, visible ratio graph
% energy resolution (+as a function of E)
% gamma beam energy에 따라 backsplash가 만드는 event veto
% + incident angle에 따라?
Figure \ref{fig:EMshower} shows shower profiles in X-Z plane (right) and Y-Z plane (middle), those are accumulated energy deposit on each strips for 10,000 gammas of energy as 1 GeV.
%longitudinal (right) and lateral (left) shower development for 1 GeV photon entering perpendicular to the detector surface $(\theta~=0)$). 
Its longitudinal projection (left in Fig.\ref{fig:EMshower}) %roduced by gamma of energy as $E_0$ 
can be expressed by two parameters $\alpha$ and $\beta$ as %{ref:E. Longo, I. Sestili, Nucl. Instrum. Meth. 128 (1975) 283 }
\begin{equation}
    F(E,t)=E_0\cdot (bt)^{a-1}e^{-bt}/\Gamma(a),
    %F(E,t)=E_0\cdot t^{\alpha}e^{-\beta t},
\end{equation}
where t is the z-position in radiation length. It is natural that the distributions on converter and counter are identical. 
%When we consider detector response for large number of gamma, it is needed another contribution $t_0$ which is the starting position of shower generation. Then the equation 1 becomes as
%\begin{equation}
    %F(E,t)=E_0\cdot b(bt)^{a-1}e^{-bt}/\Gamma(a),
%    F(E,t,t_0)=E_0\cdot e^{-t_0 / X_0} (t-t_0)^{\alpha}e^{-\beta (t-t_0)},
%\end{equation}
%or
%\begin{equation}
    %F(E,t)=E_0\cdot b(bt)^{a-1}e^{-bt}/\Gamma(a),
%    F(E,t)= \integral { E_0\cdot e^{-t_0 / X_0} (t-t_0)^{\alpha}e^{-\beta (t-t_0)}},
%\end{equation}
%The parameters are estimated for given detector with 1 GeV $\gamma$ as a= and b=, respectively.

On the other hand, the transverse shower spread is interpreted as a distribution of energy deposit in crossing positions of the X- and the Y-strips in neighbouring two layers as shown in Figure XXX.  This distribution is expressed by the Molière radius defined as 
\begin{equation}
\rho_M= 21.2~{\rm MeV}\cdot X_0 /E_c,
\end{equation}
where $X_0$ is the radiation length and $E_c$ is the critical energy of the detector, respectively. 
For the sampling calorimeter consisting of different materials, let us define the Molière radius as the radius of cylinder containing 90\% of shower energy. As shown in Figure xxx, the test model (1-mm lead and 5-mm scintillator) shows $\rho_M=70$ mm in average which changes with the shower depth. 
That is, we can expect an improvement on separating two gammas closely incident to the calorimeter. We will study on this subject and not treat in this paper.
%the For the detector consisting of 1mm lead and 5mm plastic scintillator contain 90\% of energy deposit inside the cylinder of radius of $\rho_M=70$ mm. %It had better to compare with CsI crystal

The energy resolution of the sampling calorimeter is mainly determined by the fluctuation of the visible ratio defined as 
\begin{equation}
R = { \frac{E_{act}} {E_{act}+E_{pas}}},
\end{equation}
where $E_{act}$ and $E_{pas}$ are energy deposit to the active and passive part of the calorimeter, respectively. This visible ratio is roughly given by a ratio of material budget between the converter and the counter. 
%is simply given by the fraction of the active component to that of the passive component, and its fluctuation becomes large when the ratio is small.
%by thickness of the converter. It is because the energy deposit at the active component is done through not only passage of the electron-positron pair but also low energy process such as compton scattering not reach to the active counter. 
As shown in Fig.~\ref{fig:energy_res}, the mean of the visible ratio for the configuration of 1-mm lead and 5-mm scintillator is  0.35 and its energy resolution is expected 4\% for 1 GeV photon. However, the visible ratio can be improved with the same amount of composed materials when we use thinner layers. Figure YYY shows the change of the visible ratio for the same ratio $R=t_{lead}/t_{scin}$=0.2 according to the thickness of the converter (thinner scintillator too). When we make the lead sheet thinner as a factor of 5, the visible ratio improves as XXX. This is because the number of low energy electrons and positrons penetrating the lead sheet. Even though the small improvement on the visible ratio, the energy resolution improved greatly with the thinner layer.
%This energy resolution is improved as a result thinner converter and counter keeping the visible ratio constant.

\begin{figure}[!hbt]
%\includegraphics[width=0.85\textwidth]{figures/Sec2/EMshower.pdf}
%\includegraphics[width=0.85\textwidth]{figures/Sec2/ang_conf.pdf}
\includegraphics[width=0.48\textwidth]{figures/Sec2/ShowerProfileZ.pdf}
\includegraphics[width=0.48\textwidth]{figures/Sec2/ShowerProfileXZ.pdf}
\caption{Profile of the EM shower in Z axis(left) and X-Z plane(right)  }
\label{fig:EMshower}
\end{figure}

\begin{figure}[!hbt]
\includegraphics[width=0.48\textwidth]{figures/3.2/moliere_radius.pdf}
\includegraphics[width=0.48\textwidth]{figures/3.2/visible_ratio.pdf}
\caption{Dependence of Moliere radius(left) and visible ratio(right) on the thickness of scintillators}
\label{fig:moliere_vis}
\end{figure}

\begin{figure}[!hbt]
\includegraphics[width=0.48\textwidth]{figures/3.2/eres_thickness.pdf}
\includegraphics[width=0.48\textwidth]{figures/3.2/energy_resolution.pdf}
\caption{The dependence of the energy resolution on the thickness of scintillators(left) and the incident energy of $\gamma$(right)}
\label{fig:energy_res}
\end{figure}

@@

%\subsection{Detector dimension}
\subsection{Angle reconstruction using Machine Learning}

Figure~\ref{fig:angle_reco_def} shows the reconstructed $\theta$ obtained from the test samples, which are generated for fixed angles in range of $\theta=$ 5 to $\theta=$ 30 in 5 degrees steps. The number of generated gammas is $10^5$ and their energy is 1 GeV. The $\XGB$ correctly reconstructs $\theta=$ with a typical resolution as 1.2 degrees. There is no significant difference according to the incident angle.

\begin{figure}[!hbt]
\includegraphics[width=0.89\textwidth]{figures/Fig1_reco_def.pdf}
\caption{ (Color online) Reconstructed $\theta$ with respect to each true incident $\theta$ dotted lines denote each Gaussian function fitting the reconstructed $\theta$ distribution. The standard deviation of all Gaussian functions are estimated to be 1.3 degree.}
\label{fig:angle_reco_def}
\end{figure}

\begin{figure}[!hbt]
\includegraphics[width=0.58\textwidth]{figures/Fig2_reco_Width_width.pdf}
\caption{ The angular resolution as a function of the scintillator strip width for 1 GeV $\gamma$. The incident angle for each simulation is fixed as 10 degree.  }
\label{fig:angle_reco_width}
\end{figure}

>>>>

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{lineno}
\usepackage{xspace}
\usepackage{cleveref}
\usepackage {xcolor}

@@

\begin{document}
\setcounter{page}{0}
\title[]{ MC-based feasibility study of new sampling calorimeter for measuring the $\gamma$ incident }

@@

\section{Motivation}
\label{sec:mot}
The electromagnetic calorimeter has played an important role in experimental studies on the nuclear and particle physics.  
% experiments specially to detect gamma. 
Various crystals have been developed for better energy and timing resolution of the detector so far~\cite{Calorimeter}. %The most important properties of the detector are good energy and timing resolution, and various crystals has been developed for the purpose[] .
On the other hand, the sampling calorimeter becomes popular in large-scale high energy experiment mainly due to its cost-effectiveness. The sampling calorimeter consists of alternating passive converters that generate the electromagnetic shower and active counters that obtain information on it. Since the energy-deposit in the passive convert can not be measured, its fluctuation, called sampling fluctuation, determines the energy resolution of the  calorimeter, which is generally worth than that of the detector made of crystals.
%mainly determined by the  which causes a limitation of energy resolution,  
%Even though the energy deposit in the passive converter is not detected which is related to the 
%measuring energy deposit of the shower particles tends to replace the crystal calorimeter in large-scale high energy experiment[].
%Due to the fluctuation of energy deposit in the converter, sampling fluctuation, the sampling calorimeter suffers poor energy resolution. 
It is possible, however, to optimize configuration of a large-size detector by selecting the converters and the counters among various candidates those are easily fabricated with low costs. A 5m-long cylindrical calorimeter made of alternating lead and plastic scintillating plates is an example of the sampling calorimeter~\cite{E391a_barrel}.

%The active counter can be selected as an easily fabricated in large size with relatively low cost such as the plastic scintillator~\cite{E391a_barrel}. %In addition, the fluctuation becomes not so important for high energy gammas owing to large number of shower particles. %When we use a plastic scintillator as a counter, we can fabricate a large scale of calorimeter with relatively low cost.  
%There are many efforts to develop new types of calorimeter, and a fine-segmented sampling calorimeter is in the line[].

A layer structure of the sampling calorimeter enables us to measure the individual profiles of the shower along to the accumulating direction, and we can estimate the direction of incident gamma by connecting the center of them. When we  decide momentum vector of incident $\gamma$ by using only the calorimeter, it is expected more reliable event reconstruction with better background rejection. In a particular experiment, KOTO, aiming to detect the final state existing only single $\pi^0$ without any other particles, the experimental method will be an important tool for the successful measurement.

%Even though the sampling fluctuation makes limitation on the energy resolution in this energy range, there is a merit to construct momentum vector of $\gamma$ by using only the calorimeter without additional

%We studied a possible detector configuration to measure incident direction of gamma with energies in a range from hundred MeV to few GeV. 
%measure not only energy but also incident angle of photon. Considering a stochastic process in shower generation, there is a certain limitation of the detection resolution. Also, the effect of the sampling fluctuation is a matter in medium energy photons in range 100 MeV to few GeV photons. 
 %information about its generation position. Since the $  Participating in event reconstruction

%experiment to have a motivation on developing a detector configuration enable to measure the incident direction.

@@

Considering negligibly small detection efficiency on neutrinos, the $K_L \rightarrow \pi^0 \nu \bar{\nu}$ decay is defined as an event existing only single $\pi^0$ in the final sate, which is reconstructed by detecting two gammas generated from prompt decay of the $\pi^0$. The KOTO utilizes undoped Cesium Iodide (CsI) crystals to measure the incident energies and positions of the $\gamma$~\cite{CsI}. %An hermetic detector system surrounding decay region confirms that there is no any particles accompanying the two photons. 
In order to reconstruct $\pi^0$ from the detected two $\gamma '$s, we need an assumption that they are generated from the single $\pi^0$ decaying at the beam axis. This assumption works correctly with $K_L$ beam having small-size cross-section and hermetic veto counters assuring the two-$\gamma$ final state

There are, however, large amount of background events have a possibility to become the two-$\gamma$ final state because of various reasons. For example, the $K_L \rightarrow \pi^0 \pi^0$ decay will be the two-$\gamma$ event when we can not detect additional two $\gamma$'s due to limited detection efficiency of detectors. Considering the 8 orders of larger branching ratio of the $K_L \rightarrow \pi^0 \pi^0$ decay compared to that of the $K_L \rightarrow \pi^0 \nu \bar{\nu}$, it is a challenging to achieve the required detection efficiency which is closely connected to the achievable experimental sensitivity in terms of accidental loss. If the remained two $\gamma$'s are generated from different $\pi^0$, the reconstructed $\pi^0$ will be differ from another results from obtained by newly obtained the momentum vectors. We can reject so-called odd-pairing  of the $K_L \rightarrow \pi^0 \pi^0$ decays.
%without strict veto requirement.
%strict detection efficiency of the additional $\gamma$'s.

In addition, small fraction of neutrons those are dominant component of the $K_L$, can interact with detectors and produce $\pi^0$ or two-$\gamma$-like events. Those events are rejected by the shower shape analysis looking into energy sharing among the finely segmented CsI crystals, and the rejection power will be greatly improved if we could use the additional information on the $\gamma$'s.

%$contaminated

%considerable background event still be the two-$\gamma$ final state

%There as in addition to the detection variables. This means that we would get a wrong $\pi^0$ in case the assumption is not correct any more, but there is no information to figure out, unfortunately. With a new information, incident angle, we can judge a validity of the reconstructed $\pi^0$.
%In order to reconstruct a  $\pi^0$ from obtained information of the two gammas 
%In reality, energies and positions of two photons measured at the EM-Cal are not enough to reconstruct the $\pi^0$, and we need an assumption that they are generated from the $\pi^0$ decaying at the beam axis. This reconstruction would be failed in case the assumption is not correct any more, but there is no information to figure out, unfortunately. 
% In addition to the current reconstruction of $\pi^0$, we can extract its decay position independently with the angle measurement. By requiring a consistency between two vertices reconstructed with different observables, we can select genuine single $\pi^0$ decay rejecting wrong pairs due to various sources such as odd-pairing of $K_L \rightarrow \pi^0 \pi^0$ decays, neutron induced two clusters, and so on. It also enables us to remove $\pi^0$ and $\eta$ decays produced by halo neutrons because they occur far from the beam axis. We can expect similar rejection against $K_L \rightarrow \gamma \gamma$ decays when the $K_L$ deviate form the beam center due to scattering.

%For the angle measurement of gamma, we should get information about the spatial profile of shower particles generated in the EM-Cal. This will be realized by recording energy deposit to the cell of detector separately, which are finely segmented in three dimensions. 
Since the electromagnetic shower development is a stochastic process, there should be a limitation on the resolution of the measurement. We have studied about the angle measure with a sampling calorimeter consisting of alternating lead sheets and strips of plastic scintillator. The have performed an feasibility study on the angle measurement to estimate feasibility  achievable angular resolution in ballpark figure and clarify the items we have to solve for better performance.

%the angular measurement of incident gamma. %could be a good candidate of the calorimeter as describe in this paper.
In the following section, the configuration of detector and Monte Carlo simulation for electromagnetic shower generation will be given. In the section III, we will describe how to reconstruct incident angle from the generated detector response by using one of the most attractive toolkit of the machine learning; $\XGB$. Finally, we will summarize our study briefly.

\section{ELECTROMAGNETIC SHOWER}
We started the study with a detector setup consisting of alternating lead sheet as the passive converter and strips of the plastic scintillator as the active counter. % as shown in Fig.~\ref{fig:det_conf}. The electromagnetic shower mainly generated at the lead sheet (passive component) due to its short radiation length ($X_0 = 5.6~{\rm mm})$ and the information of the shower particles is obtained by using the scintillator (active  component). 
The thickness of lead is 1 mm and scintillator is 5 mm, respectively. The lead sheet has a cross-section of  500 mm $\times$ 500 mm and each scintillator strips of 500 mm $\times$ 15 mm  being arranged along the X- and Y-direction alternatively along Z-direction as shown in  Fig.~\ref{fig:det_conf}. Total number of alternating layers is 105 which corresponds to 20 radiation length (20 Xo) and possible to contain all of the shower particles generated by $\gamma$ in the region of medium energy (from  100 MeV to few GeV).

@@

The generation of incident $\gamma$ and its interaction with detector materials was simulated by using the GEANT4 package (ver. xxx) with the standard EM sub-packages~\cite{GEANT4}.
The $\gamma$ entered the center of the detector and moved to the positive direction of Z-axis, where the surface of the first layer is defined as a starting point (Z=0). Its incident angle is defined as the polar angle ($\theta$) along to the Z-direction, that is, $\theta = 0$ for the $\gamma$ enters perpendicular to the detector surface. %The generated energies are in range from hundred MeV to few GeV which is interested to the KOTO experiment. 
Figure~\ref{fig:Evt_Dis} shows a typical event display describing the energy deposit to the each scintillator strips in both of X-Z and Y-Z plane for 1-GeV $\gamma$ entering in perpendicular to the center of the detector ($\theta=0$ and $\phi=0$). %We can get an three-dimensional information on the shower development combining them and will use them as inputs of the machine learning package, $\XGB$. 
%This information indicates the shower development, and will be used as an input of the machine learning package, $\XGB$. 
%We can get the shower profiles from energy deposits in individual strips arranged in the 3-dimension. Figure XXX shows a event display for 1 GeV gamma entering with $\theta =0$ in X-Z and Y-Z planes. The amount of energy deposit to each strips are expressed by the darkness (color online).

\begin{figure}[!hbt]
%\includegraphics[width=0.85\textwidth]{figures/Sec2/ang_conf.pdf}
\includegraphics[width=0.45\textwidth]{figures/EventDisplay.jpg}
\includegraphics[width=0.45\textwidth]{figures/EventDisplay.jpg}

\caption{Distribution of energy deposit to the each scintillator strips in X-Z plane (Left) and Y-Z plane (Right) for 1-GeV $\gamma$ entering perpendicularly to the detector ($\theta=0$ and $\phi=0$).}
\label{fig:Evt_Dis}
\end{figure}

%With the configuration, we can get shower profiles in X- and Y-axis in turn, and estimate the incident angle from the

%energies are in range from hundred MeV to few GeV by considering the KOTO experiment.

%its origin is defined as the centers of the central strips both of the X- and Y- There generation position is the centers of both of the X- and Y- strip moves along with Z-direction and its incident angle was defined as a polar angle to the direction.  With the configration, we can get shower profiles in X- and Y-axis in turn, and estimate the incident angle from them.%The electromagnetic showers are generated with given detector setup by using the GEANT4 package (ver. xxx) with the standard EM sub-packages ~\cite{GEANT4}.

@@

%\subsection{Properties of generated shower}
% moliere rad, visible ratio graph
% energy resolution (+as a function of E)
% gamma beam energy에 따라 backsplash가 만드는 event veto
% + incident angle에 따라?
%Figure \ref{fig:EMshower} shows shower profiles in X-Z plane (right) and Y-Z plane (middle), those are accumulated energy deposit on each strips for 10,000 gammas of energy as 1 GeV.
%longitudinal (right) and lateral (left) shower development for 1 GeV photon entering perpendicular to the detector surface $(\theta~=0)$).

%Figure~\ref{fig:EMshower} shows side (left) and top view (right) of energy deposit in the each strips for $\gamma$ entering the center of the detector with energy of 1 GeV and incident angle of 10 degrees and azimuthal angle of 0 degree . By using this profiles along with the alternating X- and Y-direction, we can reconstruct incident angle of the $\gamma$ after studying its nature with the $\XGB$ package.

The GRANT4 can provide reliable results on the electromagnetic shower produced by the incident $\gamma$. 
%by usis well produced by showers show typical distributions both of longitudinal and transverse directions. Figure~\ref{fig:Longitudinal} shows longitudinal distribution of average sum of the energy deposit in strips of each counter layers regardless the direction of arrangement. %Considering the EM shower is generated mainly at the converter, the both distributions of the converter and counter are identical and can be expressed by two parameters, 
Its longitudinal profile depends on incident energy and can be expressed \cite{Longo} by the three parameters as following;
%When we ignore large radiation of the scintillator, the profile can
%projection (left in Fig.\ref{fig:EMshower}) %roduced by gamma of energy as $E_0$ 
%can be expressed by two parameters $\alpha$ and $\beta$ as %{ref:E. Longo, I. Sestili, Nucl. Instrum. Meth. 128 (1975) 283 }
\begin{equation}
    F(E,t)=A  t^\alpha e^{-bt},
    %F(E,t)=E_0\cdot t^{\alpha}e^{-\beta t},
\end{equation}
where t is the position of scintillator strips along the Z-direction. As shown in Fig.~\ref{fig:Longitudinal}, the Eq. 1 describes the obtained average energy deposit on each layer of scintillator strips reasonably. In the case of the sampling calorimeter, however, the energy deposit on the converters and counters is caused by multiple processes and its fraction is changed along with the shower develpoment.
%is changed according to the shower depth because there is a change of energy depositing process. 
%and uwe focus only on the energy deposit 
%the probability of the shower generation is much different between the counter and converter.
As a result, the ratio of the energy deposit in counter and in converter changes according to the layer position as shown in Fig.~\ref{fig:Longitudinal} (right).% because there are multiple process of which probability changes according to development.
In order to describe the shower profile in the sampling calorimeter, we need to take into account the layer dependent of the energy deposit. Since we will use the simulated results only for current study on angle measurement, we did not proceed any further analytic study on the process.
%As a results, the Eq. 1 needs an additional correction factor ... to express the obtained results more correctly. %We can take into account the changes by using layer-by-layer structure of the detector.   %({\it Shall we investigate energy dependency of the parameters ?)}% Considering the EM shower is generated mainly at theIt is natural that the distributions on converter and counter are identical. 
%When we consider detector response for large number of gamma, it is needed another contribution $t_0$ which is the starting position of shower generation. Then the equation 1 becomes as
%\begin{equation}
    %F(E,t)=E_0\cdot b(bt)^{a-1}e^{-bt}/\Gamma(a),
%    F(E,t,t_0)=E_0\cdot e^{-t_0 / X_0} (t-t_0)^{\alpha}e^{-\beta (t-t_0)},
%\end{equation}
%or
%\begin{equation}
    %F(E,t)=E_0\cdot b(bt)^{a-1}e^{-bt}/\Gamma(a),
%    F(E,t)= \integral { E_0\cdot e^{-t_0 / X_0} (t-t_0)^{\alpha}e^{-\beta (t-t_0)}},
%\end{equation}
%The parameters are estimated for given detector with 1 GeV $\gamma$ as a= and b=, respectively.

\begin{figure}[!hbt]
%\includegraphics[width=0.85\textwidth]{figures/Sec2/EMshower.pdf}
%\includegraphics[width=0.85\textwidth]{figures/Sec2/ang_conf.pdf}
\includegraphics[width=0.48\textwidth]{figures/LongProfile.jpg}
\includegraphics[width=0.48\textwidth]{figures/LayerVisibleRatio.jpg}+
\caption{Generated average energy deposit on the scintillator strips along Z axis(left) and visible ratio for each layer.}
\label{fig:Longitudinal}
\end{figure}

On the other hand, the lateral spread of the shower
%is interpreted as a distribution of energy deposit in crossing positions of the X- and the Y-strips in neighbouring two layers.  This spread 
is expressed as the the Molière radius defined ~\cite{PDG} as 
\begin{equation}
R_M= 21.2~{\rm MeV}\cdot X_0 /E_c,
\end{equation}
where $X_0$ is the radiation length and $E_c$ is the critical energy of the detector, respectively. 
Since the sampling calorimeter contains different materials placed at the different localized positions, we defined the $R_M$ as the radius of cylinder containing 90\% of the energy deposit instead of using the Eq. (2). The left panel of Figure~\ref{fig:Moliere_vis} shows energy deposit per each layer (black line) and integrated energy deposit up to the layers. We can deduce the Molière radius as 70 mm, which is largely depends on the position of its measurement. The right panel of Figure~\ref{fig:Moliere_vis} shows the radius as a function of scintillator layer, which increases along the shower depth. The first three bins show large radius because of large contribution of shower particles generated opposite to the incident direction.

%difference of $\rho_M$ for different configurations of the detector and its dependency on the detector layer. We need to notice the spread of shower is different along to the its development similar to the ratio of the energy deposit mentioned above. We can take into account the complicated response of the sampling calorimeter by using the individual energy deposit of the strips as inputs of the machine learning for the angle reconstruction.

\begin{figure}[!hbt]
\includegraphics[width=0.44\textwidth]{figures/Edep_R.jpg}
\includegraphics[width=0.48\textwidth]{figures/Moliere_layer.jpg}
\caption{Left:Energy deposit for given radius as a differential(black line) and integral distribution(red line) Right: Moliere radius as a function of ID of scintillator-strip layers.}
\label{fig:Moliere_vis}
\end{figure}

With the detector configuration shown in Fig.~\ref{fig:det_conf}, we can get three dimensional information on the showers. By using the obtained data as an input of the machine learning package, we can extract the incident angle of the $\gamma$ as explained following section. 
%When we apply the three dimensional information on the generated shower profile, we can reconstruct incident $\gamma$ more correctly by integrating the energy deposit. 
%For simplicity in numerical calculation, %For the sampling calorimeter consisting of different materials, 
%let us define the Molière radius as the radius of cylinder containing 90\% of shower energy. As shown in Fig.~\ref{fig:Moliere_vis}, the configuration of 1-mm lead and 5-mm scintillator shows $\rho_M=70$ mm in average which changes with the shower depth. %That is, we can expect an improvement on separating two gammas closely incident to the calorimeter. We will study on this subject and not discuss any more in this paper.
%the For the detector consisting of 1mm lead and 5mm plastic scintillator contain 90\% of energy deposit inside the cylinder of radius of $\rho_M=70$ mm. %It had better to compare with CsI crystal

%The energy resolution of the sampling calorimeter is mainly determined by the fluctuation of the visible ratio defined as 
%\begin{equation}
%R = { \frac{E_{act}} {E_{act}+E_{pas}}},
%\end{equation}
%where $E_{act}$ and $E_{pas}$ are energy deposit to the active and passive part of the calorimeter, respectively. This visible ratio is roughly given by the ratio of material budget between the converter and the counter. 
%is simply given by the fraction of the active component to that of the passive component, and its fluctuation becomes large when the ratio is small.
%by thickness of the converter. It is because the energy deposit at the active component is done through not only passage of the electron-positron pair but also low energy process such as compton scattering not reach to the active counter. 
%As shown in Fig.~\ref{fig:energy_res}, the mean of the visible ratio for the configuration of 1-mm lead and 5-mm scintillator is  0.35 and its energy resolution is expected 4\% for 1 GeV photon. However, the visible ratio can be improved with the same amount of composed materials when we use thinner layers. Figure YYY shows the change of the visible ratio for the same ratio $R=t_{lead}/t_{scin}$=0.2 according to the thickness of the converter (thinner scintillator too). When we make the lead sheet thinner as a factor of 5, the visible ratio improves as XXX. This is because the number of low energy electrons and positrons penetrating the lead sheet is increased in case of thinner converter. As a result of the increasing probability, the sampling fluctuation becomes small and the energy resolution improved as a result.
%This energy resolution is improved as a result thinner converter and counter keeping the visible ratio constant.

%\begin{figure}[!hbt]
%\includegraphics[width=0.48\textwidth]{figures/3.2/eres_thickness.pdf}
%\includegraphics[width=0.48\textwidth]{figures/3.2/energy_resolution.pdf}
%\caption{Visible ratio of the sampling calorimeter for different configuration (Left) and energy resolution as a function of incident $\gamma$ energy (right).}
%\label{fig:energy_res}
%\end{figure}

@@

\section{ANGLE RECONSTRUCTION}
\label{sec:res}

The incident angle of the $\gamma$ can be estimated as a results of machine learning by using the $\XGB$, which is one of the popular packages supporting a scalable tree boosting system~\cite{xgboost:2016}. We used energy deposits on each scintillator strips as input data for the $\XGB$, and the packages connects the relationship among the input data to estimate the incident angle. ** a little detail one or two senteces***

%are deposit energies on each scintillator strip by the generated shower particles. It includes the strips of zero-energy deposit in order to satisfy the requirement that the number of input data should be identical. As the training procedure, the $\XGB$ studies profiles of energy deposit to the individual strips with respect to the incident angle for a given $\gamma$ energy.  ({\it This part should be updated)}

For the training of the $\XGB$, we generated $\gamma$'s uniformly in the range 0 to 50 degrees of polar angle ($\theta$) and  0 to 360 degrees of azimuthal angle ($\varphi$) for given energy (training sample). By using another data set (testing sample) which was generated at a fixed polar angle, we estimated performance of angular reconstruction of the detector. The number of generated $\gamma$ was
$2\times10^5$ for the training sample and $1\times10^5$ for the testing sample, respectively.

@@

%\subsection{Detector dimension}
%\subsection{Angle reconstruction using Machine Learning}

%With the results of the $\XGB$ by using the training sample generated with the uniform distributions in both of polar and azimuthal angles, we estimated the incident angle of photons generated with a fixed value for a given energy. 
Figure~\ref{fig:angle_10degree} shows the distribution of reconstructed angles for 1-GeV $\gamma$ entered detector with 10 degrees of incident angle. %The Gaussian distribution (black solid line) provides the proper mean value,  the $\XGB$ can provide correct answer. 
We can get proper mean value of the distribution, however, it has heavier tail compared to that of the Gaussian distribution. In order to describe the obtained result more correctly, we tried to fit it with the Generalized Gaussian (GG) function.

\begin{figure}[!hbt]
\includegraphics[width=0.7\textwidth]{figures/GG_fit.jpg}
\caption{ (Color online) Reconstructed $\theta$ with respect to 10 degrees of incident $\theta$. The gaussian function can not describe the tail region (red dotted line). The generalized gaussian function (black solid line) shows much better agreement with the obtained result.}
\label{fig:angle_10degree}
\end{figure}
